Home

### 2015-10-26 analysis/index.Rmd
add more analyses

*  [Make coverage tables](summarize_coverage.html)

>>>>

*  [Investigate coverage of hu method without penalty](investigate_hu_badcoverage.html)
*  [Run mixfdr on low noise bimodal situation](check_mixfdr_lownoise.html)
*  [Make coverage tables](summarize_coverage.html)

## DSC Znull (assess behaviour of ash LR under null)

* [Summarize results of null simulations](summarize_dsc_znull.html)
